### 2017-07-09 admin/IRB/performances/consent_waiver/main.tex
added acmart (and other stuff?)

\documentclass[11pt]{article}
\usepackage{balance,graphics,setspace,parskip,sourceserifpro,textcomp,titling,nameref,color,fancyhdr,paralist}
\usepackage[T1]{fontenc}
\usepackage[margin=1in,headheight=14pt]{geometry}
\usepackage[inline]{enumitem}
\usepackage[compact]{titlesec}
\PassOptionsToPackage{hyphens}{url}\usepackage[pdflang={en-US},pdftex]{hyperref}

\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=blue,
  urlcolor=red,
  breaklinks=true,
  hypertexnames=false
}
\usepackage[dvipsnames]{xcolor}

>>>>

\documentclass[11pt]{article}
\usepackage{balance,graphics,setspace,parskip,textcomp,titling,nameref,color,fancyhdr,paralist}
\usepackage[T1]{fontenc}
\usepackage[margin=1in,headheight=14pt]{geometry}
\usepackage[inline]{enumitem}
\usepackage[compact]{titlesec}
% \PassOptionsToPackage{hyphens}{url}\usepackage[pdflang={en-US},pdftex]{hyperref}

\definecolor{linkColor}{RGB}{6,125,233}
% \hypersetup{
%   bookmarksnumbered,
%   pdfstartview={FitH},
%   colorlinks,
%   citecolor=black,
%   filecolor=black,
%   linkcolor=blue,
%   urlcolor=red,
%   breaklinks=true,
%   hypertexnames=false
% }
\usepackage[dvipsnames]{xcolor}

### 2017-07-09 admin/IRB/vitae/consent/main.tex
added acmart (and other stuff?)

\documentclass[11pt]{article}
\usepackage{balance,graphics,setspace,parskip,sourceserifpro,textcomp,titling,nameref,color,fancyhdr,paralist}
\usepackage[T1]{fontenc}
\usepackage[margin=1in,headheight=14pt]{geometry}
\usepackage[inline]{enumitem}
\usepackage[compact]{titlesec}
\PassOptionsToPackage{hyphens}{url}\usepackage[pdflang={en-US},pdftex]{hyperref}

\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=blue,
  urlcolor=red,
  breaklinks=true,
  hypertexnames=false
}
\usepackage[dvipsnames]{xcolor}

@@

\newenvironment{headerfont}{\color{gray}\fontfamily{ptm}\selectfont}{}
\pagestyle{fancy}{
  \lhead{\begin{headerfont}Stanford University\end{headerfont}}
  \chead{\begin{headerfont}\textbf{\underline{Waiver of Documentation}}\end{headerfont}}
  \rhead{\textbf{Approval Date}: \underline{November 30 2016}}
}

\section*{{\LARGE Ethnographic Study of Online Performance Artists}}

\section*{What's this study about?}
We're trying to learn about
the relationships online performers have with each other and
with the
organizations that run
the platforms that they stream and
upload to.
Some of this touches on things like
dealing with inter--personal issues and
how the community deals with major events
as well as questions about what it's like to
make your income from online public performances.

@@

\section*{What else should I know?}
If you're interested in participating, you should know
\begin{compactitem}
  % \item Since it would be too difficult to get a signature from participants,
  %       (to say nothing of verifying the signature),
  %       we're using a ``\textbf{waiver of documentation}'',
  %       so this is purely informational.
  \item The first conversation will probably take 30--45 minutes.
        Later conversations (if you're okay with it) would likely be shorter
        (mostly to clarify things or ask follow--up questions).
  \item I can't compensate you (or anyone, really) for their time.
  \item I plan on recording the audio of our conversation
        so I can transcribe what you said
        (so I don't misremember or misquote anything).
        Once I have a transcript, I'll delete the audio.
\end{compactitem}

>>>>

\documentclass[10pt]{article}
\usepackage{balance,graphics,setspace,parskip,sourceserifpro,textcomp,titling,nameref,color,fancyhdr,paralist}
\usepackage[T1]{fontenc}
\usepackage[margin=1in,headheight=14pt]{geometry}
\usepackage[inline]{enumitem}
\usepackage[compact]{titlesec}

\setsansfont[BoldFont={Source Sans Pro Bold},
              Numbers={OldStyle}]{Source Sans Pro}
\setmainfont[BoldFont={Source Serif Pro Semibold},
              Numbers={OldStyle}]{Source Serif Pro}
\setmonofont{Source Code Pro}
\definecolor{linkColor}{RGB}{6,125,233}

\usepackage[dvipsnames]{xcolor}

@@

\newenvironment{headerfont}{\color{gray}\fontfamily{ptm}\selectfont}{}
\pagestyle{fancy}{
  \lhead{\begin{headerfont}Stanford University\end{headerfont}}
  \chead{\begin{headerfont}\textbf{\underline{Waiver of Documentation}}\end{headerfont}}
  \rhead{\textbf{Approval Date}: \underline{Tentative}}
}

\section*{{\LARGE Managing crowd and gig workers' histories and qualifications}}

\section*{What's this study about?}
We're trying to learn about
whether independently--run platforms for tracking workers' histories
and qualifications
can better inform whether workers are likely
to be qualified and suited for complex gig work.
Some of this research will involve
the management of workers \textbf{by} other workers.

In this study, we'll be asking workers managed by this system about
their experiences using the platform (``vitae''), as well as
interviewing people who manage these qualification groups.
% the relationships online performers have with each other and
% with the
% organizations that run
% the platforms that they stream and
% upload to.
% Some of this touches on things like
% dealing with inter--personal issues and
% how the community deals with major events
% as well as questions about what it's like to
% make your income from online public performances.

@@

\section*{What else should I know?}
If you're interested in participating, you should know
\begin{compactitem}
  \item Participation is voluntary; if you wish not to participate, it's perfectly all right.
  \item Participants will not be compensated for their interviewing time.
  \item If at any point you wish to withdraw from the study,
        we will accommodate such requests as quickly as reasonably possible.
  % \item Since it would be too difficult to get a signature from participants,
  %       (to say nothing of verifying the signature),
  %       we're using a ``\textbf{waiver of documentation}'',
  %       so this is purely informational.
  % \item The first conversation will probably take 30--45 minutes.
  %       Later conversations (if you're okay with it) would likely be shorter
  %       (mostly to clarify things or ask follow--up questions).
  % \item I can't compensate you (or anyone, really) for their time.
  % \item I plan on recording the audio of our conversation
  %       so I can transcribe what you said
  %       (so I don't misremember or misquote anything).
  %       Once I have a transcript, I'll delete the audio.
\end{compactitem}
